---
title: "hw02-Gun-Kim"
author: "Gun Yeup Kim"
date: "2017³â 10¿ù 1ÀÏ"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
  install.packages(c("dplyr","readr"),repos = "http://cran.us.r-project.org")
library(dplyr)
library(readr)
```


#2. Import the data in R

```{r}
  dat <- read.csv('nba2017-player-statistics.csv',colClasses = c(Position = "factor", Salary = "double"), stringsAsFactors = FALSE)
  str(dat)
```

```{r}
dat2 <- read_csv('nba2017-player-statistics.csv', col_types = list(Position = col_factor(levels = NULL)))
str(dat2)
```

#3. Right afte importing the data

```{r}
  #Replacing Experience to integers
  dat$Experience <- replace(dat$Experience, dat$Experience == "R", 0)
  dat$Experience <- as.integer(dat$Experience)
  str(dat)
```

#4. Performance of players

```{r}
  #add variables
  Missed_FG <- dat$FGA - dat$FGM
  Missed_FT <- dat$FTA - dat$FTM
  Total_points <- 3*dat$Points3+2*dat$Points2+dat$FTM
  REB <- dat$OREB + dat$DREB
  Min_per_game <- dat$MIN/dat$GP
  EFF = (Total_points + REB + dat$AST + dat$STL + dat$BLK - Missed_FG - Missed_FT - dat$TO)/dat$GP
  dat <- cbind(dat, Missed_FG, Missed_FT,Total_points, REB, Min_per_game, EFF)
  summary(EFF)
  hist(EFF, main = "Histogram of Efficiency (EFF)", col = "gray")
```

```{r}
  #Display the player name, team, salary, and EFF value of the top-10 players by EFF
  new_data_frame_top_10 <- dat[order(-dat$EFF),]
  new_data_frame_top_10 <- slice(new_data_frame_top_10,1:10)
  new_data_frame_top_10 <- select(new_data_frame_top_10, Player, Team, Salary, EFF)
  new_data_frame_top_10
  
```

```{r}
  #provide the names of the players that have a negative EFF
  negative_EFF_Player <- filter(dat, EFF < 0)
  negative_EFF_Player
```

```{r}
  #compute the correlation coefficients between EFF and all the variables used in the EFF
  cor_Total_points <- cor(dat$Total_points, dat$EFF)
  cor_REB <- cor(dat$REB, dat$EFF)
  cor_STL <- cor(dat$STL, dat$EFF)
  cor_AST <- cor(dat$AST, dat$EFF)
  cor_BLK <- cor(dat$BLK, dat$EFF)
  cor_Missed_FT <- cor(dat$Missed_FT, dat$EFF)*(-1)
  cor_Missed_FG <- cor(dat$Missed_FG, dat$EFF)*(-1)
  cor_TO <- cor(dat$TO, dat$EFF)*(-1)
  
  data_frame_for_Correlation_EFF <- data.frame(c(PTS = cor_Total_points, REB = cor_REB, STL = cor_STL, AST = cor_AST, BLK = cor_BLK, Missed_FT = cor_Missed_FT, Missed_FG = cor_Missed_FG, TO = cor_TO))
  Correlation_EFF <- (c(cor_Total_points,cor_REB,cor_STL,cor_AST,cor_BLK,cor_Missed_FT, cor_Missed_FG, cor_TO))
  cols <- c("red", "gray")[(Correlation_EFF > 0)+1]
  barplot(Correlation_EFF, names.arg = c("PTS","REB","STL","AST","BLK","Missed_FT","Missed_FG","TO"), cex.names = 0.7, main = "Correlations between Player Stats and EFF", col = cols)


```


# 5. Efficiency and Salary
```{r}
  #Efficiency and Salary
  plot(dat$EFF, dat$Salary, main = "Scatterplot for Player2", xlab = "EFF", ylab = "Salary")+lines(lowess(dat$EFF,dat$Salary), col = "red")
  cor(dat$EFF, dat$Salary)
```

#Efficiency and salary are positivly correlated. 

```{r}
  #Create another data frame for MPG >20
  players2 <- filter(dat, Min_per_game >20)
  plot(players2$EFF, players2$Salary)+lines(lowess(players2$EFF,players2$Salary), col ="red")
  cor(players2$EFF, players2$Salary)
```
#This data frame also shows that efficiency and salary are positivly correlated but the correlation between these two are little bit smaller than all players' data. 

#6. Comments and Reflections
#filtering was confusing because of NA
#ploting was easy because we did a lot of practice
#It took me about 4 hours
