---
title: "hw01-Gun-Kim"
author: "Gun Yeup Kim"
date: "2017 9 22"
output:
  github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
  #load data file
  load("nba2017-salary-points.RData")
```
# 1. A bit of data preprocessing
```{r}
  #Creating a new salary variable measured in millions of dollars, up to 2 decimal digits
  salary <- salary/1000000
  salary <- format(round(salary,2), nsmall =2)
  salary
```
```{r}
  #Replace R to 0
  experience <- replace(experience, experience == "R",0)
  experience <- as.integer(experience)
  experience
```
```{r}
  #Creating new position variable as an R factor with more decriptive labels
  position <- replace(position,position == "C", 'center')
  position <- replace(position,position == "SF", 'small_fwd')
  position <- replace(position,position == "PF", 'power_fwd')
  position <- replace(position,position == "SG", 'shoot_guard')
  position <- replace(position,position == "PG", 'point_guard')
  position <- as.factor(position)
    position
```
```{r}
  #Computing the frequencies for position
  position_frequencies <- table(position)
  position_frequencies
  ```
# 2. Scatterplot of Points and Salary
 ```{r}
  plot(points, salary, col = "red", xlab = "Points", ylab = "Salary (in millions)", main = "Scatterplot of Points and Salary")
```


# 3. Correlation between Points and Salary
```{r}
  #Creating all the variable to calculate Correlation between Points and Salary
  n <- 441
  mean_points <-  sum(points)/n
  int_salary <- as.integer(salary)
  mean_salary <- sum(int_salary)/n
  #Variance for points
  sample_minus_mean_points <- (points - mean_points)^2
  var_points <- sum(sample_minus_mean_points)/(n-1)
  #Variance for salary
  sample_minus_mean_salary <- (int_salary - mean_salary)^2
  var_salary <- sum(sample_minus_mean_salary)/(n-1)
  #Standard Deviation for points
  sd_points <- sqrt(var_points)
  #Standard Deviation for salary
  sd_salary <- sqrt(var_salary)
  #Covariance
  joint_points_salary <- (points - mean_points)*(int_salary-mean_salary)
  cov_points_salary <- sum(joint_points_salary)/(n-1)
  #Correlation bewtween points and salary
  corr_points_salary <- cov_points_salary/(sd_points*sd_salary)
  mean_points
  mean_salary
  var_points
  var_salary
  sd_points
  sd_salary
  cov_points_salary
  corr_points_salary

```

# 4.Simple Linear Regression

```{r}
  # slope
  b1 <- corr_points_salary * sd_salary/sd_points
  b0 <- mean_salary - b1*mean_points
  y_hat <- b0 + b1*points
  y_hat
  summary(y_hat)
```

```{r include=FALSE}
  #inline code 
  
  #b <- (n*sum(x*y) - sum(x)*sum(y))/(n*sum(x^2)-(sum(x)^2))
  #a <- (sum(y)-b*sum(x))/n
  #y <- a+b*x
```
'r y'

# Interpreting slope Coefficient
# B1 represents the difference in the predicted value of Y for each one-unit difference in B1. 

#Interpreting the intercept
#B0 can be interpreted as the value when you would predict for Y if b1 = 0

```{r}
  #predicted salary for 0,100,500,1000, 2000
  x <- c(0,100,500,1000,2000)
  Y_hat2 <- b0 + b1*x
  Y_hat2
```

# 5. Plotting the regression line
```{r}
require(stats)  
plot(points, salary, col = "black", xlab = "Points", ylab = "Salary (in millions)", main = "Scatterplot of Points and Salary")+
  abline(a = 1.08679969, b = 0.00857372168, col = "blue")+ text(2450,19,"Regression",pch = 1, cex = 1, col = "blue")+
  lines(lowess(points, salary), col = "red")+text(2250, 28, "lowess",pch =1, cex = 1, col = "red")
```

# 6. Regression residuals and Coefficient of Determination
```{r}
  #vector of residuals
  residuals_y <- int_salary - y_hat
  summary(residuals_y)
  #RSS
  rss <- sum(residuals_y^2)
  rss
  #TSS
  tss <- sum((int_salary - mean_salary)^2)
  tss
  #R-square
  r_square <- 1-(rss/tss)
  r_square
```

# 7. Exploring Position and Experience
```{r}
  plot(experience, salary, col = "black",xlab = "Years of Experience", ylab = "Salary (in millions)" , main = "Scatterplot with lowess smooth") + lines(lowess(experience,salary), col = "red")
```

```{r}
 #scatterplot3d
  require(scatterplot3d)
  scatterplot3d(points, experience, salary, color = "red", main = "3D Scatterplot")
  
```

# Experience and Salary do related to each other
```{r}
  # boxplot
  factor_salary <- as.factor(salary)
  boxplot(int_salary ~ position, data = position, xlab = "position", ylab = "Salary (in millions)", main = "Boxplot")
```

#Since medians for all of the position look similar, I believe salary and position are not much related to each other.

# 8. Comments and Reflections
#   1. Most of problems were workable; however, I still do not get the inline code
#   2. plotting different plots was easy
#   3. It is nice but still confusing
#   4. Same as Number 3
#   5. Yes, I did need help. I got helped from Internet sources
#   6. It took about 4 to 5 hours
#   7. For me, it was a inline code
#   8. Inline code
#   9. Not that much.
#   10. It was exciting. I feel proud of completing this assignment by myself.



